---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vecsymr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `vecsymr` is to implement Vector Symbolic Architecture (VSA)
primitives to support experimentation. It is intended to be a simple VSA
implementation (the VSA equivalent of the geneticist's fruit fly) to providse a
convenient base for experimentation. The design choices are
[my]{https://www.rossgayler.com} personal preferences to support my research.
The initial emphasis is on functionality and flexibility with no specific
concern for performance. There is no intention to put this package on CRAN.

I believe that phasor VSAs (where the  vector elements are unit magnitude
complex numbers) are the best choice for basic VSAs. However, I have initially
imported functions for bipolar VSAs from

[VSA_altitude_hold]{https://github.com/rgayler/VSA_altitude_hold} to provide
some code while I get the hang of writing an R package. Once the package
contains enough phasor VSA code I will probably remove the bipolar VSA code.
The phasor VSA code will probably include some extra features to support
non-negativity and experimentation with clean-up memory.

## Installation

You can install the development version of `vecsymr` from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rgayler/vecsymr")
```

The current implementation is experimental. I expect the functional content to
evolve as I work out what I want this package to do. I also expect the API to
evolve as I work out how to make it easier to work with. If you want to do any
reproducible work with the package you will need to use something like
[{renv}](https://rstudio.github.io/renv/) to freeze the version in use.

## Ignore below here

Everything after this point is just boilerplate to be edited.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(vecsymr)
## basic example code
```

## Remember

You'll still need to render `README.Rmd` regularly, to keep `README.md`
up-to-date. `devtools::build_readme()` is handy for this. You could also use
GitHub Actions to re-render `README.Rmd` every time you push. An example
workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

If you create figures in the README don't forget to commit and push the
resulting figure files, so they display on GitHub.
